Implementing simplified INLA into `aghq`

### 2022-10-25 src/dev_sinla/sinla.Rmd
Add KS tests for all i = 1:30 #16

M <- 1000
samples_jointgaussianmarginal <- rnorm(M, mean_i, sqrt(var_i))

ecdf_jointgaussianmarginal <- ecdf(samples_jointgaussianmarginal)
grid <- seq(min(samples_jointgaussianmarginal), max(samples_jointgaussianmarginal), by = 0.1)

plot_cdf2 <- plot_cdf +
  geom_line(
    data = data.frame(x = grid, y = ecdf_jointgaussianmarginal(grid)),
    aes(x = x, y = y), col = cbpalette[1]
  )

@@

```{r}
ks_jointgaussianmarginal_tmbstan <- inf.utils::ks_test(samples_tmbstan, samples_jointgaussianmarginal)
ks_jointgaussianmarginal_tmbstan
```

The maximum difference between the two ECDFS is `r ks_jointgaussianmarginal_tmbstan$D` which occurs at the point `r ks_jointgaussianmarginal_tmbstan$l`.

@@

kable_data <- data.frame(
  "Distance" = c(ks_jointgaussianmarginal_tmbstan$D, ks_laplace_tmbstan$D),
  "Location" = c(ks_jointgaussianmarginal_tmbstan$l, ks_laplace_tmbstan$l)
)

rownames(kable_data) <- c("$\\text{KS}(\\texttt{tmbstan}, \\texttt{jointgaussianmarginal})$", "$\\text{KS}(\\texttt{tmbstan}, \\texttt{laplace})$")

@@

out <- lapply(1:dat$n, xi_laplace_marginal)

laplace_df <- bind_rows(out, .id = "index") %>%
  mutate(index = as.numeric(index))
```

@@

gaussian_df <- lapply(1:length(mean), function(i) {
  x <- seq(-5, 5, length.out = 1000)
  mean_i <- as.numeric(mean[i])
  sd_i <- as.numeric(sqrt(Sigma[i, i]))
  data.frame(index = i, x = x, pdf = dnorm(x, mean = mean_i, sd = sd_i))
}) %>%
  bind_rows()
```

@@

>>>>

M <- 1000
samples_gaussian <- rnorm(M, mean_i, sqrt(var_i))

ecdf_gaussian <- ecdf(samples_gaussian)
grid <- seq(min(samples_gaussian), max(samples_gaussian), by = 0.1)

plot_cdf2 <- plot_cdf +
  geom_line(
    data = data.frame(x = grid, y = ecdf_gaussian(grid)),
    aes(x = x, y = y), col = cbpalette[1]
  )

@@

```{r}
ks_gaussian_tmbstan <- inf.utils::ks_test(samples_tmbstan, samples_gaussian)
ks_gaussian_tmbstan
```

The maximum difference between the two ECDFS is `r ks_gaussian_tmbstan$D` which occurs at the point `r ks_gaussian_tmbstan$l`.

@@

kable_data <- data.frame(
  "Distance" = c(ks_gaussian_tmbstan$D, ks_laplace_tmbstan$D),
  "Location" = c(ks_gaussian_tmbstan$l, ks_laplace_tmbstan$l)
)

rownames(kable_data) <- c("$\\text{KS}(\\texttt{tmbstan}, \\texttt{gaussian})$", "$\\text{KS}(\\texttt{tmbstan}, \\texttt{laplace})$")

@@

laplace_df <- lapply(1:dat$n, xi_laplace_marginal) %>%
  bind_rows(.id = "index") %>%
  mutate(index = as.numeric(index))

M <- 1000

samples_laplace <- lapply(1:1:dat$n, function(i) {
  samples <- approxfun(laplace_df$cdf, laplace_df$theta)(runif(M))
  data.frame("value" = samples)
}) %>%
  bind_rows(.id = "index")
```

@@

gaussian_df <- lapply(1:dat$n, function(i) {
  x <- seq(-5, 5, length.out = 1000)
  mean_i <- as.numeric(mean[i])
  sd_i <- as.numeric(sqrt(Sigma[i, i]))
  data.frame(index = i, x = x, pdf = dnorm(x, mean = mean_i, sd = sd_i))
}) %>%
  bind_rows()

samples_gaussian <- lapply(1:dat$n, function(i) {
  mean_i <- as.numeric(mean[i])
  sd_i <- as.numeric(sqrt(Sigma[i, i]))
  samples <- rnorm(M, mean_i, sd_i)
  data.frame("value" = samples)
}) %>%
  bind_rows(.id = "index")
```

@@

### KS test

```{r}
ks_gaussian_tmbstan <- lapply(1:length(mean), function(i) {
  samples_gaussian_i <- filter(samples_gaussian, index == i)$value
  samples_tmbstan_i <- filter(samples_tmbstan, index == i)$value
  inf.utils::ks_test(samples_gaussian_i, samples_tmbstan_i)
})

ks_laplace_tmbstan <- lapply(1:length(mean), function(i) {
  samples_laplace_i <- filter(samples_laplace, index == i)$value
  samples_tmbstan_i <- filter(samples_tmbstan, index == i)$value
  inf.utils::ks_test(samples_laplace_i, samples_tmbstan_i)
})

ks_results <- bind_rows(
  bind_rows(ks_gaussian_tmbstan, .id = "index") %>%
    mutate(type = "gaussian"),
  bind_rows(ks_laplace_tmbstan, .id = "index") %>%
    mutate(type = "laplace")
)

ks_results %>%
  select(index, D, type) %>%
  pivot_wider(
    names_from = type,
    values_from = D
  ) %>%
  ggplot(aes(x = laplace, y = gaussian)) +
    geom_point(alpha = 0.5) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
    lims(x = c(0, 1), y = c(0, 1)) +
    labs(x = "KS(laplace, tmbstan)", y = "KS(gaussian, tmbstan)") +
    theme_minimal()
```
